# Literature

A vital part of the water cycle is fresh surface water. One of the great challenges in maintaining water quality is controlling the amount of nutrients it contains. The ways in which nutrients reach the aquatic ecosystem are varied. These can come from the atmosphere, groundwater, the discharge of rivers and streams, and the discharge of sewage. Although nutrients are essential for aquatic ecosystems, an excess can led to pollution, such as the algal blooms, an excessive increase in the number of algae, very common in lakes and reservoirs. Increased pollution due to algal blooms in large freshwater bodies is a problem throughout the world. The empirical correlation between total phosphorus (TP) and chlorophyll a (Chl-a) have been used to develop simple models and guide management decisions since the 1960s [@stow2013chlorophyll] [@yuan2020rethinking]. However, the use of these models is limited by the inexactness in this correlation in particular lakes [@yuan2020rethinking]. There have been numerous studies related to TP and Chl-a with other parameters as fundamental for the control of the algal bloom in lakes. The parameters used in these studies are total suspended solids [@yuan2020rethinking], Secchi Disk depth [@brown1998seasonal;@heiskary1988developing], and nitrogen [@filstrup2017relationship]. It is clear that phosphorus influences algal blooms, but the effect of other pollutants and environmental parameters are not clearly understood and may have equal or more importance.To understand what is really happening inside a lake and to find possible solutions, a complete data collection and analysis of the data are necessary for each particular freshwater body. 

The state of Utah has several bodies of fresh water. The first pioneer settlements, which began in the mid-19th century, found the necessary water resources to live in this arid area. However, the appearance of definitive settlements produced a change in land use, impacting ecosystems, including the aquatic one. The first recorded signs of water contamination date from the year 1948 and are from Utah Lake (UL), where contamination was found in different areas due to the lack of sewage trapping [@deseret1948pollution]. The first efforts to control algal blooms have been on phosphorus, since it was considered the limiter. Nitrogen seems to be more limited than phosphorus, principally in high and dry areas, as Utah Lake would be [@merritt2004utah]. In search of a solution to this and other water quality problems (and following the United States Environmental Protection Agency (EPA) goals), the Utah Department of Water Quality (DWQ) has been working in water quality data collection. A study of all the data gathered using statistical tools through an open-source software for data science can lead to important discoveries.

```{r setup, include=FALSE}
source(here::here("code/setup.R"))
```

```{r import, include=FALSE}
source(here::here("code/import.R"))
```

## Data Import
`r total_param` parameters of the UL data available from the DWQ from the years 2017, 2018, and 2019 are analyzed in this report. 

```{r echo=FALSE}
knitr::kable(
  head(data_orig), caption = 'Example of the data',  
  booktabs = TRUE)%>% 
  kable_styling(latex_options="scale_down") %>%
  scroll_box(width = "100%", box_css = "border: 0px;")
```
```{r include=FALSE}
#number of stations
ul<-data[!duplicated(data$Longitude), ]
total_stations<-nrow(ul)
```

The data, that include data from `r total_stations` stations, were downloaded in October of 2020. 

```{r mapa, echo=FALSE}
#map and markers
ul%>%
  leaflet() %>%
  setView(lng=-111.83, lat=40.15, zoom=10)%>%
  addTiles()%>%
  addMarkers(lng = ~Longitude, lat= ~Latitude, popup= ~LocationName)
```

The available data are from April to November. These data were divided by station and filtered by year and month. The data from the same month was averaged. However, there are months in which there are no Chl-a data.The table 2.2 shows the processed data for the station 4917500. 

```{r table, include=FALSE}
source(here::here("code/table.R"))
```


```{r datos500, echo=FALSE}
#Table with station4917500 data
knitr::kable(
  head(data4917500,20), caption = 'Station 4917500 data',
  booktabs = TRUE
)
```