
```{r setup-meth, include=FALSE}
source(here::here("code/setup.R"))
```

```{r import-meth, include=FALSE}
source(here::here("code/import.R"))
```

```{r table-meth, include=FALSE}
source(here::here("code/table.R"))
```

# Data

## Data Import
`r total_param` parameters of the UL data available from the DWQ from the years 2017, 2018, and 2019 were analyzed in this report. 

```{r include=FALSE}
#number of stations
ul<-data[!duplicated(data$Longitude), ]
total_stations<-nrow(ul)
```

The data, that include data from `r total_stations` stations, were downloaded in October of 2020. 

```{r mapa, echo=FALSE}
#map and markers
ul%>%
  leaflet() %>%
  setView(lng=-111.83, lat=40.15, zoom=10)%>%
  addTiles()%>%
  addMarkers(lng = ~Longitude, lat= ~Latitude, popup= ~LocationName)
```

The available data were from April to November. These data were divided by station and filtered by year and month. The data from the same month was averaged. The table 3.1 shows the processed data for the station 4917500. 

```{r table, include=FALSE}
source(here::here("code/table.R"))
```

```{r datos500, echo=FALSE}
#Table with station4917500 data
knitr::kable(
  head(data4917500,20), caption = 'Station 4917500 data',
  booktabs = TRUE
)%>%
  kable_classic(full_width = T, html_font = "Cambria")%>%
  footnote(c("Chla: Chlorophyll-a,",
              "DO: Dissolved Oxygen,",
              "DN: Dissolved Nitrogen,",
              "TN: Total Nitrogen,",
              "DP: Dissolved Phosphate-phosphorus,",
              "TP: Total Phosphate-phosphorus,",
              "TW: Temperature, water,",
              "TDS: Total Dissolved Solids,",
              "Turb: Turbidity"),
           footnote_as_chunk = T)
```

## Data Quality 

After analyzed the data of each station, there were many missing values found for the Chl-a parameter. Due to the fact that the station 4917450 was the only one that does not have missing values, all the analysis of this project was performed with this specific data set. To be able to compare the monthly average per year, we kept only the months from May to September (table 3.2).

```{r data-450, echo=FALSE}
#data from station 4917450, months 5,6,7,8, and 9
#show table
data450<-data4917450[!(data4917450$month=="04" | data4917450$month=="10" | data4917450$month=="11"),]
knitr::kable(
  head(data450,20), caption = 'Station 4917450 data',
  booktabs = TRUE)%>%
  kable_classic(full_width = T, html_font = "Cambria")%>%
  footnote(c("Chla: Chlorophyll-a,",
              "DO: Dissolved Oxygen,",
              "DN: Dissolved Nitrogen,",
              "TN: Total Nitrogen,",
              "DP: Dissolved Phosphate-phosphorus,",
              "TP: Total Phosphate-phosphorus,",
              "TW: Temperature, water,",
              "TDS: Total Dissolved Solids,",
              "Turb: Turbidity"),
           footnote_as_chunk = T)
```

As it can be seen in table 3.2, there were not missing values in the station 4917450. The data was properly formatted and classified. In the following table, we can see the parameters statistics:

```{r, echo=FALSE}
#Data station 4917450 statistics
data_sum<-select(data450,-Year,-month)
summary(data_sum)
```

The statistics show that, for the Chl-a, the mean is 12% bigger than the median. This means that the distribution is non-normal. We can also see in the Chlorophyll-a Distribution graph that the probability distribution of the Chlorophyll-a is positive skewed. In this case, the Spearman Method is used to analyze the parameter.

```{r, echo=FALSE}
#Chla distribution
ggplot(data=data450, aes(Chla)) + 
  geom_histogram(binwidth=65, colour="black", fill="purple", boundary = 65)+
  labs(title='Chlorophyll-a Distribution', x='Chlorophyll-a')
```

