
```{r setup-meth, include=FALSE}
source(here::here("code/setup.R"))
```

```{r import-meth, include=FALSE}
source(here::here("code/import.R"))
```

```{r table-meth, include=FALSE}
source(here::here("code/table.R"))
```

# Data

## Data Import
`r total_param` parameters of the UL data available from the DWQ from the years 2017, 2018, and 2019 are analyzed in this report. 

```{r echo=FALSE}
knitr::kable(
  head(data_orig), caption = 'Example of the data',  
  booktabs = TRUE)%>% 
  kable_styling(latex_options="scale_down") %>%
  scroll_box(width = "100%", box_css = "border: 0px;")
```
```{r include=FALSE}
#number of stations
ul<-data[!duplicated(data$Longitude), ]
total_stations<-nrow(ul)
```

The data, that include data from `r total_stations` stations, were downloaded in October of 2020. 

```{r mapa, echo=FALSE}
#map and markers
ul%>%
  leaflet() %>%
  setView(lng=-111.83, lat=40.15, zoom=10)%>%
  addTiles()%>%
  addMarkers(lng = ~Longitude, lat= ~Latitude, popup= ~LocationName)
```

The available data are from April to November. These data were divided by station and filtered by year and month. The data from the same month was averaged. However, there are months in which there are no Chl-a data. The table 2.2 shows the processed data for the station 4917500. 

```{r table, include=FALSE}
source(here::here("code/table.R"))
```

```{r datos500, echo=FALSE}
#Table with station4917500 data
knitr::kable(
  head(data4917500,20), caption = 'Station 4917500 data',
  booktabs = TRUE
)%>%
  kable_classic(full_width = F, html_font = "Cambria")
```

## Data Quality 
After analyzed the data of each station, there were many missing values found for the chl-a parameter. Due to the fact that the station 4917450 is the only one that does not have missing values, all the analysis of this project is going to be performed with this specific data set. To be able to compare the monthly average per year, we kept only the months from May to September. The names of the columns were simplified (table 3.1)

```{r rename-meth, include=FALSE}
source(here::here("code/rename.R"))
```

```{r data-450, echo=FALSE}
#data from station 4917450, months 5,6,7,8, and 9
#show table
data450<-data4917450[!(data4917450$month=="04" | data4917450$month=="10" | data4917450$month=="11"),]
knitr::kable(
  head(data450,20), caption = 'Station 4917450 data',
  booktabs = TRUE)%>%
  kable_classic(full_width = F, html_font = "Cambria")
```

As it can be seen in table 3.1, there are not missing values in the station 4917450. The data is properly formatted and classified. In the following table, we can see the parameters statistics:

```{r, echo=FALSE}
#Data station 4917450 statistics
data_sum<-select(data450,-Year,-month)
summary(data_sum)
```

The probability distribution of the Chlorophyll-a is positive skewed. The Spearman Method must be used to analyze the correlation between parameters.

```{r, echo=FALSE}
#Chla distribution
ggplot(data=data450, aes(Chla)) + 
  geom_histogram(binwidth=75, colour="black", fill="white")+
  labs(title='Chlorophyll-a Distribution', x='Chlorophyll-a')
```

The Spearman Method must be used to analyze the correlation between parameters.