# Methods

```{r setup, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
library(leaflet)
library(rprojroot)
```

```{r import, include=FALSE}
source(here::here("code/import.R"))
```

```{r table, include=FALSE}
source(here::here("code/table.R"))
```

```{r datos450, echo=FALSE}
knitr::kable(
  head(data4917450,20), caption = 'Station 4917450 data',
  booktabs = TRUE
)
```
We describe our methods in this chapter.

Here is a review of existing methods.

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

(Table copied)

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
