# Results

```{r setup-results, include=FALSE}
source(here::here("code/setup.R"))
```

```{r import-results, include=FALSE}
source(here::here("code/import.R"))
```

```{r table-results, include=FALSE}
source(here::here("code/table.R"))
```

```{r rename-results, include=FALSE}
source(here::here("code/rename.R"))
```

```{r data-450, include=FALSE}
#data from station 04917450, months 5,6,7,8, and 9
data450<-data4917450[!(data4917450$month=="04" | data4917450$month=="10" | data4917450$month=="11"),]
```
Using the Spearman Method, the correlation coefficients between all the parameters show a strong positive correlation between the Total Phosphorus (TP) and the Chlorophyll-a (Chl-a) and a strong negative correlation between the Total Phosphorus (TP) and the Dissolved Oxygen (DO)
```{r heat-map, echo=FALSE}
#heat map with all the parameters
x = data450[,c(3:10)]
ggcorr(x, nbreaks = 20, mid = "white", high="darkred", label=T, method = c('pairwise','spearman'))
```
To understand better what is the correlation between Chl-a and TP, the following graph shows the values of Chl-a in function of the values of the TP
```{r chla-TP, echo=FALSE}
#Chla vs TP plot
ggplot(data450, aes(x=TP, y=Chla))+
  geom_point(aes(color=month))+
  geom_smooth()
```
From the graph, we can see that the positive correlation between the TP and Chl-a is stronger for values of TP between 0.40 and 0.65 mg/l.

Because TN is considered another primary nutrient to the production of algal bloom, and because the correlation coefficient between Chl-a and TN is low, a time series graph between Chl-a, TP, and TN is performed to see if the TN  is also influencing.

```{r data-timeseries, include=FALSE}
#data matrix for the time series, Date = year-month-day
data_serie<-data%>%
  filter(LocationID==4917450)%>%
  select(Date, Characteristic, Value)%>%
  group_by(Date, Characteristic)%>%
  summarise(mean_value=mean(Value))%>%
  spread(Characteristic, mean_value)%>%
  arrange(Date)%>%
  rename(DO= 'Dissolved oxygen (DO)')%>%
  rename(DN='Nitrogen Dissolved')%>%
  rename(TN='Nitrogen Total')%>%
  rename(DP='Phosphate-phosphorus Dissolved')%>%
  rename(TP='Phosphate-phosphorus Total')%>%
  rename(Chla='Chlorophyll a Total')%>%
  rename(Turb='Turbidity')%>%
  rename(TDST='Total dissolved solids Total')%>%
  rename(TW='Temperature, water')
```

```{r series-TN, echo=FALSE}
#Time series with TN
ggplot(data_serie, aes(x=Date))+
    geom_point(aes(y=TP, color="TP"))+
    geom_line(aes(y=TP, color="TP"))+
    geom_point(aes(y=Chla/150, color="Chl-a"))+
    geom_line(aes(y=Chla/150, color="Chl-a"))+
    geom_point(aes(y=TN/2, color="TN"))+
    geom_line(aes(y=TN/2, color="TN"))+
    geom_hline(yintercept=0.4, color='black')+
    geom_hline(yintercept=0.65, color='black')
```
The time series analysis shows that when the TN too high, the Chl-a decreases, even though the TP has value between 0.4 and 0.65 mg/l.
The positive correlation between the TN and Chl-a is for values of TN between 0.60 and 1.10 mg/l. 
```{r chla-TN, echo=FALSE}
#Chla vs TN plot
ggplot(data450, aes(x=TN, y=Chla))+
  geom_point(aes(color=month))+
  geom_smooth()
```
Because the TP and DO have a strong negative correlation, the time series analysis is performed to see the relationship between these too variables and the Chl-a.

```{r series-DO, echo=FALSE}
#Time series with DO
ggplot(data_serie, aes(x=Date))+
    geom_point(aes(y=TP, color="TP"))+
    geom_line(aes(y=TP, color="TP"))+
    geom_point(aes(y=Chla/150, color="Chl-a"))+
    geom_line(aes(y=Chla/150, color="Chl-a"))+
    geom_point(aes(y=DO/12, color="DO"))+
    geom_line(aes(y=DO/12, color="DO"))+
    geom_hline(yintercept=0.4, color='black')+
    geom_hline(yintercept=0.65, color='black')
```
```{r chla-DO, echo=FALSE}
#Chla vs DO plot
ggplot(data450, aes(x=DO, y=Chla))+
  geom_point(aes(color=month))+
  geom_smooth()
```
```{r TP-DO, echo=FALSE}
#TP vs DO plot
ggplot(data450, aes(x=TP, y=DO))+
  geom_point(aes(color=month))+
  geom_smooth()
```

```{r boxplot-chla, fig.cap='Chlorophyll a distribution by month', out.width='80%', fig.asp=.75, fig.align='center', echo=FALSE}
boxplot(Chla~month,data=data450)
```
